---
title: "Simple functions"
author: "Bastola"
date: "`r format(Sys.Date(), ' %B %d %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      collapse = TRUE, 
                      comment=NA, 
                      warning = FALSE,
                      message = FALSE,
                      fig.height = 4, fig.width = 6, fig.align='center')

library(tidyverse) 
library(stringr)
library(tidytext)
library(gutenbergr)
library(wordcloud)
library(magrittr)
library(ggthemes)
```


## Your turn 1

The variance of a random variable $x$ is defined as: 

$$\operatorname{Var}(x)=\frac{1}{n-1} \sum_{i=1}^{n}\left(x_{i}-\bar{x}\right)^{2}$$

where $x_i = (\sum_i^n x_i)/n$] is the sample mean. Also, the skewness of the random variable $x$ is defined as:

$$\operatorname{Skew}(x)=\frac{\frac{1}{n-2}\left(\sum_{i=1}^{n}\left(x_{i}-\bar{x}\right)^{3}\right)}{\operatorname{Var}(x)^{3 / 2}}$$

Please write functions to calculate the variance and skewness of $\{12, 45, 54, 34, 56, 30, 67, \text{NA}\}$.

```{r}
x <- c(12, 45, 54, 34, 56, 30, 67, NA)
```


### a.

```{r}
# function to calculate the variance of a vector

var <- function(x){
  x <- na.omit(x) # omit NA values
  sum((x - mean(x)) ^ 2) / (length(x) - 1)
}

```


```{r}
var(x)
```


### b. 

```{r}
# function to calculate the skewness of a vector

skewness <- function(x) {
  x <- na.omit(x) # omit NA values
  sum((x - mean(x)) ^ 3) /((length(x) - 2) * var(x) ^ (3 / 2))
}

```


```{r}
skewness(x)
```

-----------------------------------

# Your turn 2

```{r, warning=TRUE}
func <- function(x) {
  if( length(x) < 2 ){warning("need string with atleast two characters")}else{
    str_c(str_sub(x,1,1), collapse = ":")
  }
}

# using str_c()
func1 <- function(x){
  if( length(x) < 2 ){warning("need string with atleast two characters")}else{
    str_c(str_sub(x,1,1), collapse = ":")
  }
}


x0 <- c()
x1 <- c("a")
x2 <- c("a","b")
x3 <- c("a","b","c","d")

func(x3)
func1(x3)
```


-----------------------------------------

## Your turn 3


```{r}
# Function to take the book id of books from project Gutenberg 
# Return a data tibble with smart words and their counts, sorted

word_count <- function(book_id) {
    my_favorite_book <- gutenberg_download(book_id) %>% 
    mutate(linenumber=row_number()) %>% 
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort=TRUE)
my_favorite_book
}

```


### a. Go to [Project Gutenberg](https://www.gutenberg.org/) website and search the book ID of your favorite book. If you don't have a favorite book , try `1633`. What is the most used word in this book?


```{r}
book1 <- word_count(book_id = 1633)   
```



### b. Make a function that takes the data tibble  and the maximum number of words to plot in a word cloud as an argument and output the wordcloud as a plot.


```{r}
plot_word_cloud <- function(mybook, max_words){
  wordcloud(words= mybook$word,freq =  mybook$n, max.words = max_words)
}
```



```{r}
plot_word_cloud(book1, 200)
```

### c. Modify the `word_count()` function so that it outputs words starting with a particular alphabet. You can do this by adding an argument to the function that takes the starting string as an argument.


```{r}
word_count_modified <- function(book_id, begin) {
    my_favorite_book <- gutenberg_download(book_id) %>% 
    mutate(linenumber=row_number()) %>% 
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort=TRUE) %>%
    filter(str_detect(word, str_glue("^[",{begin},"]")))  
my_favorite_book
}
```


```{r}
book2 <- word_count_modified(245, "e")
plot_word_cloud(book2, 10)
```


